---
title: "CTET_Behaviour_Results_v5"
author: "Elaine P."
date: "29/04/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(ggplot2)
library(ggpubr)
library(car)
library(haven)
library(data.table)
library(visreg)
library(dplyr)
library(tidyr)
library(reshape2)
library(rstatix)
library(JWileymisc)
library(lme4)
library(lmerTest)
library(multilevelTools)

#library(ggstance)
#library(jtools)
#library(broom.mixed)
#library(sjPlot)
#library(glmmTMB)

library(lattice)

#library(arm)

library(plyr)
library(Rmisc)
#library(plotly)

library(cowplot) 
library(dplyr) 
library(readr)


CTET_Behaviour1 <- read.csv("../Tables/CTET_behav_resblock_full.txt")

CTET_Behaviour1$SubID<-as.factor(CTET_Behaviour1$SubID)
CTET_Behaviour1$Treatment<-as.factor(CTET_Behaviour1$Treatment)
CTET_Behaviour1<-CTET_Behaviour1[as.numeric(CTET_Behaviour1$BlockN)<11,]
CTET_Behaviour1$BlockN<-as.numeric(CTET_Behaviour1$BlockN)
CTET_Behaviour1$Treatment<-relevel(CTET_Behaviour1$Treatment,"PLA")
CTET_Behaviour1<-CTET_Behaviour1[!is.na(CTET_Behaviour1$BlockN),]

```

```{r}
##False Alarm
lm.FA0 <- lmer(FA ~ 1 + (1|SubID), data = CTET_Behaviour1, REML = FALSE)

##Effects of treatment on false alarms 
lm.FA1 <- lmer(FA ~ 1 + Treatment + (1|SubID), data = CTET_Behaviour1, REML = FALSE)

#Added effects of block number on false alarm
lm.FA2 <- lmer(FA ~ 1 + Treatment + BlockN + (1|SubID), data = CTET_Behaviour1, REML = FALSE)

#Added effects of block number as an interaction on false alarm
lm.FA3 <- lmer(FA ~ 1 + Treatment * BlockN + (1|SubID), data = CTET_Behaviour1, REML = FALSE)

##Anova to see which one has the most interaction
anova(lm.FA0,lm.FA1,lm.FA2,lm.FA3)
lm.FA2 <- lmer(FA ~ 1 + Treatment + BlockN + (1|SubID), data = CTET_Behaviour1, REML = TRUE)
summary(lm.FA2)
confint(lm.FA2, method = "Wald", oldNames = FALSE)

## Normality plot of residuals - TA: Try to plot QQ plots
hist(residuals(lm.FA2))
qqnorm(resid(lm.FA2))
qqline(resid(lm.FA2))
plot(lm.FA2)
plot(fitted(lm.FA2), resid(lm.FA2))
binnedplot(fitted(lm.FA2),resid(lm.FA2))
```
- lm.FA2 was the winning model (AIC and BIC)
- ATM and BlockN had sig (***) effects on FA 
```{r}
##Misses 
lm.Miss0 <- lmer(Miss ~ 1 + (1|SubID), data = CTET_Behaviour1, REML = FALSE)

##Effects of treatment on misses
lm.Miss1 <- lmer(Miss ~ 1 + Treatment + (1|SubID), data =  CTET_Behaviour1, REML = FALSE)

##Added effects of block number on misses 
lm.Miss2 <- lmer(Miss ~ 1 + Treatment + BlockN + (1|SubID), data =  CTET_Behaviour1, REML = FALSE)

##Added effects of block number as an interaction on misses 
lm.Miss3 <- lmer(Miss ~ 1 + Treatment*BlockN + (1|SubID), data =  CTET_Behaviour1, REML = FALSE)

##Anova to see which one has the most interaction
anova(lm.Miss0,lm.Miss1,lm.Miss2,lm.Miss3)
lm.Miss2 <- lmer(Miss ~ 1 + Treatment + BlockN + (1|SubID), data =  CTET_Behaviour1, REML = TRUE)
summary(lm.Miss2)
confint(lm.Miss2, method = "Wald", oldNames = FALSE)

##Normality plot of residuals 
hist(residuals(lm.Miss2))
boxplot(residuals(lm.Miss2))
qqnorm(resid(lm.Miss2))
qqline(resid(lm.Miss2))
plot(lm.Miss2)
plot(fitted(lm.Miss2), resid(lm.Miss2))

binnedplot(fitted(lm.Miss2),resid(lm.Miss2))
```
-Although lm.Miss3 is the winning model, after Bonferonni correction, it does not sig any more (p > .00556) (NOTE: THIS WAS PREVIOUS ANALYSIS BUT STILL STANDS)
- using lm.Miss2 as sig model 
- note as well, BIC (takes into consideration complexity of model) says lm.Miss2 is winning model
- everything is sig (***) except ATM
```{r}
##Hit Rate  
lm.HR0 <- lmer(Hit_RT ~ 1 + (1|SubID), data = CTET_Behaviour1, REML = FALSE)

##Effects of treatment on hit rate 
lm.HR1 <- lmer(Hit_RT ~ 1 + Treatment + (1|SubID), data = CTET_Behaviour1, REML = FALSE)

##Added effects of block number on hit rate  
lm.HR2 <- lmer(Hit_RT ~ 1 + Treatment + BlockN + (1|SubID), data = CTET_Behaviour1, REML = FALSE)

##Added effects of block number as an interaction on hit rate  
lm.HR3 <- lmer(Hit_RT ~ 1 + Treatment*BlockN + (1|SubID), data = CTET_Behaviour1, REML = FALSE)

##Anova to see which one has the most interaction
anova(lm.HR0,lm.HR1,lm.HR2,lm.HR3)
lm.HR1 <- lmer(Hit_RT ~ 1 + Treatment + (1|SubID), data = CTET_Behaviour1, REML = TRUE)
summary(lm.HR1)
confint(lm.HR1, method = "Wald", oldNames = FALSE)

## Normality plot of residuals 
hist(residuals(lm.HR1))
boxplot(residuals(lm.HR1))
qqnorm(residuals(lm.HR1))
qqline(resid(lm.HR1))
plot(lm.HR3)
plot(fitted(lm.HR1), resid(lm.HR1))
binnedplot(fitted(lm.HR1), resid(lm.HR1))
```
- lm.HR1 is the winning model (AIC and BIC)
- All treatments were sig: ATM (**), CIT (*), and MPH (***)
```{r}
##SD Hit Rate  
lm.SDHR0 <- lmer(STD_RT ~ 1 + (1|SubID), data = CTET_Behaviour1, REML = FALSE)

##Effects of treatment on hit rate 
lm.SDHR1 <- lmer(STD_RT ~ 1 + Treatment + (1|SubID), data = CTET_Behaviour1, REML = FALSE)

##Added effects of block number on hit rate  
lm.SDHR2 <- lmer(STD_RT ~ 1 + Treatment + BlockN + (1|SubID), data = CTET_Behaviour1, REML = FALSE)

##Added effects of block number as an interaction on hit rate  
lm.SDHR3 <- lmer(STD_RT ~ 1 + Treatment*BlockN + (1|SubID), data = CTET_Behaviour1, REML = FALSE)

##Anova to see which one has the most interaction
anova(lm.SDHR0,lm.SDHR1,lm.SDHR2,lm.SDHR3)
lm.SDHR1 <- lmer(STD_RT ~ 1 + Treatment + (1|SubID), data = CTET_Behaviour1, REML = TRUE)
summary(lm.SDHR1)
confint(lm.SDHR1, method = "Wald", oldNames = FALSE)

## Normality plot of residuals 
hist(residuals(lm.SDHR1))
boxplot(residuals(lm.SDHR1))
qqnorm(residuals(lm.SDHR1))
qqline(resid(lm.SDHR1))
plot(lm.SDHR1)
plot(fitted(lm.SDHR1), resid(lm.SDHR1))
binnedplot(fitted(lm.SDHR1), resid(lm.SDHR1))
```
- lm.SDHR1 was the winning model (AIC and BIC)
- only MPH was sig (***)

```{r}
##dprime 
lm.dprime0<- lmer(dprime ~ 1 + (1|SubID), data = CTET_Behaviour1, REML = FALSE)

##Effects of treatment on dprime 
lm.dprime1 <- lmer(dprime ~ 1 + Treatment + (1|SubID), data = CTET_Behaviour1, REML = FALSE)

##Added effects of block number on dprime 
lm.dprime2 <- lmer(dprime ~ 1 + Treatment + BlockN + (1|SubID), data = CTET_Behaviour1, REML = FALSE)

##Added effects of block number as an interaction on dprime 
lm.dprime3 <- lmer(dprime ~ 1 + Treatment*BlockN + (1|SubID), data = CTET_Behaviour1, REML = FALSE)

##Anova to see which one has the most interaction
anova(lm.dprime0,lm.dprime1,lm.dprime2,lm.dprime3)


lm.dprime2 <- lmer(dprime ~ 1 + Treatment + BlockN + (1|SubID), data = CTET_Behaviour1, REML = FALSE)
summary(lm.dprime2)
confint(lm.dprime2, method = "Wald", oldNames = FALSE)

## Normality plot of residuals 
hist(residuals(lm.dprime2))
boxplot(residuals(lm.dprime2))
qqnorm(residuals(lm.dprime2))
qqline(resid(lm.dprime2))
plot(lm.dprime2)
plot(fitted(lm.dprime2), resid(lm.dprime2))
binnedplot(fitted(lm.dprime2), resid(lm.dprime2))


lm.dprime3 <- lmer(dprime ~ 1 + Treatment*BlockN + (1|SubID), data = CTET_Behaviour1, REML = FALSE)
summary(lm.dprime3)
confint(lm.dprime3, method = "Wald", oldNames = FALSE)

## Normality plot of residuals 
hist(residuals(lm.dprime3))
boxplot(residuals(lm.dprime3))
qqnorm(residuals(lm.dprime3))
qqline(resid(lm.dprime3))
plot(lm.dprime3)
plot(fitted(lm.dprime3), resid(lm.dprime3))
binnedplot(fitted(lm.dprime3), resid(lm.dprime3))


```
- lm.dprime3 is the winning model according to AIC, but to BIC it is lm.dprime2
- lm.dprime2
  - everything was sig: BlockN (**), MPH (***), CIT (**). ATM (*)
- lm.dprime3
  - CIT was sig (*) and BlockN (***)
  - MPH*BlockN sig (**)

```{r}
##criterion 
lm.crit0<- lmer(crit ~ 1 + (1|SubID), data = CTET_Behaviour1, REML = FALSE)

##Effects of treatment on criterion 
lm.crit1 <- lmer(crit ~ 1 + Treatment + (1|SubID), data = CTET_Behaviour1, REML = FALSE)

##Added effects of block number on criterion 
lm.crit2 <- lmer(crit ~ 1 + Treatment + BlockN + (1|SubID), data = CTET_Behaviour1, REML = FALSE)

##Added effects of block number as an interaction on criterion 
lm.crit3 <- lmer(crit ~ 1 + Treatment*BlockN + (1|SubID), data = CTET_Behaviour1, REML = FALSE)

##Anova to see which one has the most interaction
anova(lm.crit0,lm.crit1,lm.crit2,lm.crit3)


lm.crit2 <- lmer(crit ~ 1 + Treatment + BlockN + (1|SubID), data = CTET_Behaviour1, REML = FALSE)
summary(lm.crit2)
confint(lm.crit2, method = "Wald", oldNames = FALSE)

## Normality plot of residuals 
hist(residuals(lm.crit2))
boxplot(residuals(lm.crit2))
qqnorm(residuals(lm.crit2))
qqline(resid(lm.crit2))
plot(lm.crit2)
plot(fitted(lm.crit2), resid(lm.crit2))
binnedplot(fitted(lm.crit2), resid(lm.crit2))


lm.crit3 <- lmer(crit ~ 1 + Treatment*BlockN + (1|SubID), data = CTET_Behaviour1, REML = FALSE)
summary(lm.crit3)
confint(lm.crit3, method = "Wald", oldNames = FALSE)

## Normality plot of residuals 
hist(residuals(lm.crit3))
boxplot(residuals(lm.crit3))
qqnorm(residuals(lm.crit3))
qqline(resid(lm.crit3))
plot(lm.crit3)
plot(fitted(lm.crit3), resid(lm.crit3))
binnedplot(fitted(lm.crit3), resid(lm.crit3))


```
- AIC winning model: lm.crit3; BIC winning model: lm.crit2
- lm.crit2
  - everything sig (***) but ATM 
- lm.crit3
  - CIT was sig (**) and BlockN (***)
  -MPH*BlockN was sig (**)

```{r}
##Graph of the interaction between treatment and block number on false alarms
fa.graph <- summarySE(CTET_Behaviour1, measurevar = "FA", groupvars = c("BlockN", "Treatment"))
fa.graph$Treatment<-ordered(fa.graph$Treatment, c("PLA","MPH","ATM","CIT"))

##REFERENCE GRAPH            
ggplot(fa.graph, aes(x = BlockN, y = FA, colour = Treatment)) + geom_point() + geom_line() + scale_colour_brewer(palette = "Dark2") + scale_fill_brewer(palette = "Dark2") + ggtitle("False alarms according to block number and treatment") + ylab("False Alarms") + xlab("Block Number") + xlim(0, 10.5) + ylim(0, 0.015)

##Graph with Standard Error 
ggplot(fa.graph, aes(x = BlockN, y = FA, colour = Treatment)) + geom_point() + geom_line() + ylab("Mean False Alarms") + xlab("Block Number") + xlim(0, 10.5) + ylim(0, 0.011) + geom_ribbon(aes(ymin = FA-se, ymax = FA+se, fill = Treatment), alpha = .35, linetype = 0) + scale_fill_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) + scale_colour_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) + scale_x_continuous(breaks = c(1:10)) + scale_y_continuous(labels = scales::percent_format(accuracy = .01))+ theme_classic() +theme(panel.border = element_blank(), legend.position = "none",axis.title=element_text(size=14),axis.text=element_text(size=14), axis.title.y = element_blank())+ coord_cartesian(ylim =c(0.0009, .017))


ggsave(file="../Figures/CTET_LinePlot_FA_2021.png", 
       width = 30/2,
      height = 18/2,
    units = c("cm"))

##Barplot 
fa2.graph <- summarySE(CTET_Behaviour1, measurevar = "FA", groupvars = c( "Treatment"))
fa2.graph$FA<-fa2.graph$FA
fa2.graph$Treatment<-ordered(fa2.graph$Treatment,c("PLA","MPH","ATM","CIT"))
marks <- c(0,20000,40000,60000,80000,100000)


ggplot(data=fa2.graph, aes(x=Treatment, y=FA, fill = Treatment)) +
  geom_bar(stat="identity") + geom_errorbar(aes(ymin = FA-se, ymax = FA+se), width = .4, size = .45) + scale_fill_discrete( name = "Treatment", breaks = c("PLA", "MPH", "ATM", "CIT"), labels = c("Placebo", "Methylphenidate", "Atomoxetine", "Citalopram")) + ylab("% of Mean False Alarms")+ scale_fill_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) + scale_y_continuous(labels = scales::percent_format(accuracy = .01)) +theme_classic() +theme(legend.position = "none",axis.title=element_text(size=14),axis.text=element_text(size=14), axis.title.x = element_blank()) + coord_cartesian(ylim =c(0.0009, .017)) 

ggsave(file="../Figures/CTET_BarPlot_FA_2021.png", dpi = 600, 
       width = 15/2,
      height = 18/2,
    units = c("cm"))
```

```{r}
##Graph of the interaction between treatment and block number on missed targets
miss.graph <- summarySE(CTET_Behaviour1, measurevar = "Miss", groupvars = c("BlockN", "Treatment"), na.rm = TRUE)
miss.graph$Treatment<-ordered(miss.graph$Treatment,c("PLA","MPH","ATM","CIT"))

##Reference graph 
ggplot(miss.graph, aes(x = BlockN, y = Miss, colour = Treatment)) + geom_point() + geom_line() + scale_colour_brewer(palette = "Dark2") + scale_fill_brewer(palette = "Dark2") + ylab("Missed Target") + xlab("Block Number") + xlim(0, 12) + ylim(0, 0.5)


##Graph with Standard Error 
ggplot(miss.graph, aes(x = BlockN, y = Miss, colour = Treatment)) + geom_point() + geom_line() + ylab("Mean Missed Targets") + xlab("Block Number") + xlim(0, 11)  + geom_ribbon(aes(ymin = Miss-se, ymax = Miss+se, fill = Treatment), alpha = .35, linetype = 0) + scale_fill_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77"))  + scale_colour_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77"))+ scale_x_continuous(breaks = c(1:10)) + scale_y_continuous(labels = scales::percent_format(accuracy = 1))+ theme_classic() +theme(panel.border = element_blank(), legend.position = "none",axis.title=element_text(size=14),axis.text=element_text(size=14), axis.title.y = element_blank()) + coord_cartesian(ylim =c(.1, 0.5))

ggsave(file="../Figures/CTET_LinePlot_Misses_2021.png", 
       width = 30/2,
      height = 18/2,
    units = c("cm"))

##Barplot 
miss2.graph <- summarySE(CTET_Behaviour1, measurevar = "Miss", groupvars = c("Treatment"), na.rm = TRUE)
miss2.graph$Treatment<-ordered(miss2.graph$Treatment,c("PLA","MPH","ATM","CIT"))

ggplot(data= miss2.graph, aes(x=Treatment, y=Miss, fill = Treatment)) +
  geom_bar(stat="identity") + geom_errorbar(aes(ymin = Miss-se, ymax = Miss+se), width = .35, size = .6)  + scale_fill_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77"))  + labs (y = "% of Mean Missed Targets") + scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + coord_cartesian(ylim =c(0, 0.45))+theme_classic() + theme(legend.position = "none",axis.title=element_text(size=14),axis.text=element_text(size=14), axis.title.x = element_blank())+ coord_cartesian(ylim =c(0.1, .5)) 

ggsave(file="../Figures/CTET_BarPlot_Misses_2021.png", dpi = 600, 
       width = 15/2,
      height = 18/2,
    units = c("cm"))

```

```{r}
##Graph of the interaction between treatment and block number on hit rates
rt.graph <- summarySE(CTET_Behaviour1, measurevar = "Hit_RT", groupvars = c("BlockN", "Treatment"), na.rm = TRUE)
rt.graph$Treatment<-ordered(rt.graph$Treatment,c("PLA","MPH","ATM","CIT"))

##Reference graph
ggplot(rt.graph, aes(x = BlockN, y = Hit_RT, colour = Treatment)) + geom_point() + geom_line() + scale_colour_brewer(palette = "Dark2") + scale_fill_brewer(palette = "Dark2") + ggtitle("Mean RT for Hits according to block number and treatment") + ylab("Reaction Time") + xlab("Block Number") + xlim(0, 11) + ylim(1.3, 1.5)

##Graph with Standard Error 
ggplot(rt.graph, aes(x = BlockN, y = Hit_RT, colour = Treatment)) + geom_point() + geom_line(alpha = .7) +  ylab("Reaction Time (seconds)") + xlab("Block Number") + xlim(0, 11) + ylim(1.3, 1.5) + geom_ribbon(aes(ymin = Hit_RT-se, ymax = Hit_RT+se, fill = Treatment), alpha = .35, linetype = 0) + scale_fill_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) + scale_colour_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) +
  scale_x_continuous(breaks = c(1:10)) + theme_classic() +theme(panel.border = element_blank(), legend.position = "none",axis.title=element_text(size=14),axis.text=element_text(size=14), axis.title.y = element_blank())

ggsave(file="../Figures/CTET_LinePlot_RThits_2021.png", 
       width = 30/2,
      height = 18/2,
    units = c("cm"))

rt2.graph <- summarySE(CTET_Behaviour1, measurevar = "Hit_RT", groupvars = c("Treatment"), na.rm = TRUE)
rt2.graph$Treatment<-ordered(rt2.graph$Treatment,c("PLA","MPH","ATM","CIT"))

ggplot(data= rt2.graph, aes(x=Treatment, y=Hit_RT, fill = Treatment)) +
  geom_bar(stat="identity") + geom_errorbar(aes(ymin = Hit_RT-se, ymax = Hit_RT+se), width = .4, size = .5) + scale_fill_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) + ylim(0, 2) + labs(y = "Reaction Time (seconds)") + coord_cartesian(ylim =c(1.3, 1.5)) + scale_y_continuous(labels = scales::number_format(accuracy = .01)) + theme_classic()+theme(legend.position = "none",axis.title=element_text(size=14),axis.text=element_text(size=14), axis.title.x = element_blank())
  
ggsave(file="../Figures/CTET_BarPlot_RThits_2021.eps", dpi = 600, 
       width = 15/2,
      height = 18/2,
    units = c("cm"))
ggsave(file="../Figures/CTET_BarPlot_RThits_2021.png", dpi = 600, 
       width = 15/2,
      height = 18/2,
    units = c("cm"))
```


```{r}
##Graph of the interaction between treatment and block number on SD hit rates
sdrt.graph <- summarySE(CTET_Behaviour1, measurevar = "STD_RT", groupvars = c("BlockN", "Treatment"), na.rm = TRUE)
sdrt.graph$Treatment<-ordered(sdrt.graph$Treatment,c("PLA","MPH","ATM","CIT"))

##Reference graph
ggplot(sdrt.graph, aes(x = BlockN, y = STD_RT, colour = Treatment)) + geom_point() + geom_line() + scale_colour_brewer(palette = "Dark2") + scale_fill_brewer(palette = "Dark2") + ggtitle("SD of RT for Hits according to block number and treatment") + ylab("SD RT") + xlab("Block Number") + xlim(0, 11) 

##Graph with Standard Error 
ggplot(sdrt.graph, aes(x = BlockN, y = STD_RT, colour = Treatment)) + geom_point() + geom_line(alpha = .7) +  ylab("Standard Deviation of Reaction Time (seconds)") + xlab("Block Number") + xlim(0, 11) + geom_ribbon(aes(ymin = STD_RT-se, ymax = STD_RT+se, fill = Treatment), alpha = .35, linetype = 0) + scale_fill_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) + scale_colour_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) +
  scale_x_continuous(breaks = c(1:10)) + theme_classic() +theme(panel.border = element_blank(), legend.position = "none",axis.title=element_text(size=14),axis.text=element_text(size=14), axis.title.y = element_blank()) + ylim(0.065, .25)

ggsave(file="../Figures/CTET_LinePlot_SDRThits_2021.png", 
       width = 30/2,
      height = 18/2,
    units = c("cm"))

sdrt2.graph <- summarySE(CTET_Behaviour1, measurevar = "STD_RT", groupvars = c("Treatment"), na.rm = TRUE)
sdrt2.graph$Treatment<-ordered(sdrt2.graph$Treatment,c("PLA","MPH","ATM","CIT"))

ggplot(data= sdrt2.graph, aes(x=Treatment, y=STD_RT, fill = Treatment)) +
  geom_bar(stat="identity") + geom_errorbar(aes(ymin = STD_RT-se, ymax = STD_RT+se), width = .4, size = .5) + scale_fill_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) + labs(y = "Reaction Time Variability (seconds)") + coord_cartesian(ylim =c(0.075, .25)) + scale_y_continuous(labels = scales::number_format(accuracy = .01)) + theme_classic()+theme(legend.position = "none",axis.title=element_text(size=14),axis.text=element_text(size=14), axis.title.x = element_blank())
  
ggsave(file="../Figures/CTET_BarPlot_SDRThits_2021.eps", dpi = 600, 
       width = 15/2,
      height = 18/2,
    units = c("cm"))
ggsave(file="../Figures/CTET_BarPlot_SDRThits_2021.png", dpi = 600, 
       width = 15/2,
      height = 18/2,
    units = c("cm"))
```

```{r}
##Graph of the interaction between treatment and block number on dprime
dprime.graph <- summarySE(CTET_Behaviour1, measurevar = "dprime", groupvars = c("BlockN", "Treatment"), na.rm = TRUE)
dprime.graph$Treatment<-ordered(dprime.graph$Treatment,c("PLA","MPH","ATM","CIT"))

##Reference graph
ggplot(dprime.graph, aes(x = BlockN, y = dprime, colour = Treatment)) + geom_point() + geom_line() + scale_colour_brewer(palette = "Dark2") + scale_fill_brewer(palette = "Dark2") + ggtitle("dprime according to block number and treatment") + ylab("SD RT") + xlab("Block Number") + xlim(0, 11) 

##Graph with Standard Error 
ggplot(dprime.graph, aes(x = BlockN, y = dprime, colour = Treatment)) + geom_point() + geom_line(alpha = .7) +  ylab("dprime") + xlab("Block Number") + xlim(0, 11) + geom_ribbon(aes(ymin = dprime-se, ymax = dprime+se, fill = Treatment), alpha = .35, linetype = 0) + scale_fill_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) + scale_colour_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) +
  scale_x_continuous(breaks = c(1:10)) + theme_classic() +theme(panel.border = element_blank(), legend.position = "none",axis.title=element_text(size=14),axis.text=element_text(size=14), axis.title.y = element_blank())+ coord_cartesian(ylim =c(0.5, 5)) + scale_y_continuous(labels = scales::number_format(accuracy = .01)) 

ggsave(file="../Figures/CTET_LinePlot_dprime_2021.png", 
       width = 30/2,
      height = 18/2,
    units = c("cm"))

dprime2.graph <- summarySE(CTET_Behaviour1, measurevar = "dprime", groupvars = c("Treatment"), na.rm = TRUE)
dprime2.graph$Treatment<-ordered(sdrt2.graph$Treatment,c("PLA","MPH","ATM","CIT"))

ggplot(data= dprime2.graph, aes(x=Treatment, y=dprime, fill = Treatment)) +
  geom_bar(stat="identity") + geom_errorbar(aes(ymin = dprime-se, ymax = dprime+se), width = .4, size = .5) + scale_fill_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) + labs(y = "dprime") + coord_cartesian(ylim =c(0.5, 5)) + scale_y_continuous(labels = scales::number_format(accuracy = .01)) + theme_classic()+theme(legend.position = "none",axis.title=element_text(size=14),axis.text=element_text(size=14), axis.title.x = element_blank())
  
ggsave(file="../Figures/CTET_BarPlot_dprime_2021.eps", dpi = 600, 
       width = 15/2,
      height = 18/2,
    units = c("cm"))
ggsave(file="../Figures/CTET_BarPlot_dprime_2021.png", dpi = 600, 
       width = 15/2,
      height = 18/2,
    units = c("cm"))
```

```{r}
##Graph of the interaction between treatment and block number on criterion
criterion.graph <- summarySE(CTET_Behaviour1, measurevar = "crit", groupvars = c("BlockN", "Treatment"), na.rm = TRUE)
criterion.graph$Treatment<-ordered(criterion.graph$Treatment,c("PLA","MPH","ATM","CIT"))

##Reference graph
ggplot(criterion.graph, aes(x = BlockN, y = crit, colour = Treatment)) + geom_point() + geom_line() + scale_colour_brewer(palette = "Dark2") + scale_fill_brewer(palette = "Dark2") + ggtitle("criterion according to block number and treatment") + ylab("SD RT") + xlab("Block Number") + xlim(0, 11) 

##Graph with Standard Error 
ggplot(criterion.graph, aes(x = BlockN, y = crit, colour = Treatment)) + geom_point() + geom_line(alpha = .7) +  ylab("Criterion") + xlab("Block Number") + xlim(0, 11) + geom_ribbon(aes(ymin = crit-se, ymax = crit+se, fill = Treatment), alpha = .35, linetype = 0) + scale_fill_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) + scale_colour_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) +
  scale_x_continuous(breaks = c(1:10)) + theme_classic() +theme(panel.border = element_blank(), legend.position = "none",axis.title=element_text(size=14),axis.text=element_text(size=14), axis.title.y = element_blank()) + coord_cartesian(ylim =c(-1.3, -0.75)) + scale_y_continuous(labels = scales::number_format(accuracy = .01))

ggsave(file="../Figures/CTET_LinePlot_criterion_2021.png", 
       width = 30/2,
      height = 18/2,
    units = c("cm"))

dprime2.graph <- summarySE(CTET_Behaviour1, measurevar = "crit", groupvars = c("Treatment"), na.rm = TRUE)
dprime2.graph$Treatment<-ordered(sdrt2.graph$Treatment,c("PLA","MPH","ATM","CIT"))

ggplot(data= dprime2.graph, aes(x=Treatment, y=crit, fill = Treatment)) +
  geom_bar(stat="identity") + geom_errorbar(aes(ymin = crit-se, ymax = crit+se), width = .4, size = .5) + scale_fill_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) + labs(y = "criterion") + coord_cartesian(ylim =c(-1.3, -0.75)) + scale_y_continuous(labels = scales::number_format(accuracy = .01)) + theme_classic()+theme(legend.position = "none",axis.title=element_text(size=14),axis.text=element_text(size=14), axis.title.x = element_blank())
  
ggsave(file="../Figures/CTET_BarPlot_criterion_2021.eps", dpi = 600, 
       width = 15/2,
      height = 18/2,
    units = c("cm"))
ggsave(file="../Figures/CTET_BarPlot_criterion_2021.png", dpi = 600, 
       width = 15/2,
      height = 18/2,
    units = c("cm"))
```


```{r} 
##Raincloud plot of RT
#summary stats 
CTET_Behaviour1_noNA <-na.omit(CTET_Behaviour1)
CTET_Behaviour1_noNA$Treatment<-ordered(CTET_Behaviour1_noNA$Treatment,c("PLA","MPH","ATM","CIT"))
summary_RT <- summarySE(CTET_Behaviour1_noNA, measurevar = "Hit_RT", groupvars=c("Treatment", "SubID"))
summary_RT


 
ggplot(summary_RT, aes(x = Treatment, y = Hit_RT, fill = Treatment)) +
  geom_flat_violin(aes(fill = Treatment), position = position_nudge(x = .1, y = 0), adjust = 1.5, trim = FALSE, alpha = .25, colour = NA) + ylim(1.15,1.65) +
  geom_point(aes(x = as.numeric(Treatment)-.225, y = Hit_RT, colour = Treatment), position = position_jitter(width = .05), size = 4, shape = 20) + 
  geom_boxplot(aes(x = Treatment, y = Hit_RT, fill = Treatment), outlier.shape = NA, alpha = .5, width = .225, colour = "black") +
  scale_fill_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) + scale_colour_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) +xlab("Treatment") + ylab("RT") + theme(panel.background = element_blank(), axis.line = element_line(colour = "black"))

ggsave(file="../Figures/CTET_RainCloudPlot_RT_2021.png", 
       width = 30/2,
      height = 18/2,
    units = c("cm"))  

#code from raincloud plot: 
 geom_line(data = sumrepdat, aes(x = as.numeric(group)+.1, y = score_mean, group = time, colour = time), linetype = 3)
   geom_point(data = sumrepdat, aes(x = as.numeric(time)+.1, y = score_mean, group = group, colour = group), shape = 18) +
  geom_errorbar(data = sumrepdat, aes(x = as.numeric(time)+.1, y = score_mean, group = group, colour = group, ymin = score_mean-se, ymax = score_mean+se), width = .05)
  
 
```

```{r}
##Raincloud plot of STD_RT
#summary stats 
summary_STDRT <- summarySE(CTET_Behaviour1_noNA, measurevar = "STD_RT", groupvars=c("Treatment", "BlockN"))
summary_STDRT


ggplot(CTET_Behaviour1_noNA, aes(x = Treatment, y = STD_RT, fill = Treatment)) +
  geom_flat_violin(aes(fill = Treatment), position = position_nudge(x = .1, y = 0), adjust = 1.5, trim = FALSE, alpha = .25, colour = NA) + 
  geom_point(aes(x = as.numeric(Treatment)-.225, y = STD_RT, colour = Treatment), position = position_jitter(width = .05), size = .25, shape = 20) + 
  geom_boxplot(aes(x = Treatment, y = STD_RT, fill = Treatment), outlier.shape = NA, alpha = .5, width = .225, colour = "black") +
  geom_line(data = summary_STDRT, aes(x = as.numeric(Treatment)+.1, y = STD_RT, group = Treatment, colour = Treatment), linetype = 3, size = .6) + 
  geom_point(data = summary_STDRT, aes(x = as.numeric(Treatment)+.1, y = STD_RT, group = Treatment, colour = Treatment), shape = 18) +
  geom_errorbar(data = summary_STDRT, aes(x = as.numeric(Treatment)+.1, y =  STD_RT, group = Treatment, colour = Treatment, ymin = STD_RT-se, ymax = STD_RT+se), width = .05)+ ylim(0, 0.75) +
  scale_fill_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) + scale_colour_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) +xlab("Treatment") + ylab("Reaction Time Variability (seconds)") + theme(panel.background = element_blank(), axis.line = element_line(colour = "black"))

ggsave(file="../Figures/CTET_RainCloudPlot_STDRT_2021.png", 
       width = 30/2,
      height = 18/2,
    units = c("cm"))  
```

```{r}
##Raincloud plot of misses
#summary stats 
summary_miss <- summarySE(CTET_Behaviour1_noNA, measurevar = "Miss", groupvars=c("Treatment", "SubID"))
summary_miss

ggplot(summary_miss, aes(x = Treatment, y = Miss, fill = Treatment)) +
  geom_flat_violin(aes(fill = Treatment), position = position_nudge(x = .1, y = 0), adjust = 1.5, trim = FALSE, alpha = .25, colour = NA) + ylim(0,1) +
  geom_point(aes(x = as.numeric(Treatment)-.225, y = Miss, colour = Treatment), position = position_jitter(width = .05), size = 4, shape = 20) + 
  geom_boxplot(aes(x = Treatment, y = Miss, fill = Treatment), outlier.shape = NA, alpha = .5, width = .225, colour = "black") +
  scale_fill_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) + scale_colour_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) +xlab("Treatment") + ylab("Misses") + theme(panel.background = element_blank(), axis.line = element_line(colour = "black"))

ggsave(file="../Figures/CTET_RainCloudPlot_Miss_2021.png", 
       width = 30/2,
      height = 18/2,
    units = c("cm"))  
```
```{r}
##Raincloud plot of FA
#summary stats 
summary_FA <- summarySE(CTET_Behaviour1_noNA, measurevar = "FA", groupvars=c("Treatment", "BlockN"))
summary_FA

ggplot(CTET_Behaviour1_noNA, aes(x = Treatment, y = FA, fill = Treatment)) +
  geom_flat_violin(aes(fill = Treatment), position = position_nudge(x = .1, y = 0), adjust = 1.5, trim = FALSE, alpha = .25, colour = NA) + 
  geom_point(aes(x = as.numeric(Treatment)-.225, y = FA, colour = Treatment), position = position_jitter(width = .05), size = .25, shape = 20) + 
  geom_boxplot(aes(x = Treatment, y = FA, fill = Treatment), outlier.shape = NA, alpha = .5, width = .225, colour = "black") +
  geom_line(data = summary_FA, aes(x = as.numeric(Treatment)+.1, y = FA, group = Treatment, colour = Treatment), linetype = 3, size = .6) + 
  geom_point(data = summary_FA, aes(x = as.numeric(Treatment)+.1, y = FA, group = Treatment, colour = Treatment), shape = 18) +
  geom_errorbar(data = summary_FA, aes(x = as.numeric(Treatment)+.1, y =  FA, group = Treatment, colour = Treatment, ymin = FA-se, ymax = FA+se), width = .05)+ ylim(0, .065) +
  scale_fill_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) + scale_colour_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) +xlab("Treatment") + ylab("False Alarm") + theme(panel.background = element_blank(), axis.line = element_line(colour = "black"))

ggsave(file="../Figures/CTET_RainCloudPlot_FA_2021.png", 
       width = 30/2,
      height = 18/2,
    units = c("cm"))  
```

```{r}
##Raincloud plot of dprime
#summary stats 
summary_dprime <- summarySE(CTET_Behaviour1_noNA, measurevar = "dprime", groupvars=c("Treatment", "BlockN"))
summary_dprime

ggplot(CTET_Behaviour1_noNA, aes(x = Treatment, y = dprime, fill = Treatment)) +
  geom_flat_violin(aes(fill = Treatment), position = position_nudge(x = .1, y = 0), adjust = 1.5, trim = FALSE, alpha = .25, colour = NA) + 
  geom_point(aes(x = as.numeric(Treatment)-.225, y = dprime, colour = Treatment), position = position_jitter(width = .05), size = .25, shape = 20) + 
  geom_boxplot(aes(x = Treatment, y = dprime, fill = Treatment), outlier.shape = NA, alpha = .5, width = .225, colour = "black") +
  geom_line(data = summary_dprime, aes(x = as.numeric(Treatment)+.1, y = dprime, group = Treatment, colour = Treatment), linetype = 3, size = .6) + 
  geom_point(data = summary_dprime, aes(x = as.numeric(Treatment)+.1, y = dprime, group = Treatment, colour = Treatment), shape = 18) +
  geom_errorbar(data = summary_dprime, aes(x = as.numeric(Treatment)+.1, y =  dprime, group = Treatment, colour = Treatment, ymin = dprime-se, ymax = dprime+se), width = .05) +
  scale_fill_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) + scale_colour_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) +xlab("Treatment") + ylab("dprime") + theme(panel.background = element_blank(), axis.line = element_line(colour = "black"))

ggsave(file="../Figures/CTET_RainCloudPlot_dprime_2021.png", 
       width = 30/2,
      height = 18/2,
    units = c("cm"))  
```

```{r}
##Raincloud plot of criterion
#summary stats 
summary_crit <- summarySE(CTET_Behaviour1_noNA, measurevar = "crit", groupvars=c("Treatment", "SubID"))
summary_crit

ggplot(summary_crit, aes(x = Treatment, y = crit, fill = Treatment)) +
  geom_flat_violin(aes(fill = Treatment), position = position_nudge(x = .1, y = 0), adjust = 1.5, trim = FALSE, alpha = .25, colour = NA) + 
  geom_point(aes(x = as.numeric(Treatment)-.225, y = crit, colour = Treatment), position = position_jitter(width = .05), size = 4, shape = 20) + 
  geom_boxplot(aes(x = Treatment, y = crit, fill = Treatment), outlier.shape = NA, alpha = .5, width = .225, colour = "black") +
  scale_fill_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) + scale_colour_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) +xlab("Treatment") + ylab("criterion") + theme(panel.background = element_blank(), axis.line = element_line(colour = "black"))

ggsave(file="../Figures/CTET_RainCloudPlot_criterion_2021.png", 
       width = 30/2,
      height = 18/2,
    units = c("cm"))  
```
*** if probem occurs in geom_flat_violin : type in console: source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R") )
