---
title: "SWS_Treatment"
author: "Elaine P."
date: "19/05/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(ggpubr)
library(car)
library(haven)
library(data.table)
library(visreg)
library(dplyr)
library(tidyr)
library(reshape2)
library(rstatix)
library(JWileymisc)
library(lme4)
library(lmerTest)
library(multilevelTools)


SWS_data <- read.table("/Users/elaine/Desktop/PSY4100/LS_NeuroM/Tables/CTET_SWdetection_thr90_allE_P2P_vec.txt", header = TRUE, sep = ",", stringsAsFactors = FALSE)

```

```{r}
##Summary descriptive statistics (mean/SD, or number/frequency)
egltable(c("Drug", "SWdens", "Elec"), data = SWS_data, strict=FALSE)
```


```{r}
##Effects of drug on slow wave density
lm.sw <- lmer(SWdens  ~ 1 + Drug + (1|SubID), data = SWS_data, REML = TRUE)
summary(lm.sw)
confint(lm.sw, oldNames = FALSE)

## Normality plot of residuals 
hist(residuals(lm.sw))
boxplot(residuals(lm.sw))
```
To examine the association of treatment and slow wave density, a linear mixed model was fit. The final model included 9,216 datapoints from 37 participants. 
The standard deviation for the random intercept was 1.28 (what does this indicate about between individual differences?).
Using Satterthwaite's approximation for degrees of freedom revealed that all treatments, except MPH had a significant effect (p < .001) on false alarms. Placebo also had a significant effect (p < .05).


```{r}
##Effects of drug and electrode interaction on slow wave density
lm.swi <- lmer(SWdens  ~ 1 + Drug * Elec + (1|SubID), data = SWS_data, REML = TRUE)
summary(lm.swi)
confint(lm.swi, oldNames = FALSE)

## Normality plot of residuals 
hist(residuals(lm.swi))
boxplot(residuals(lm.swi))

```
To examine the association of treatment and its interaction with electrodes on slow wave density, a linear mixed model was fit. The final model included 9,216 datapoints from 37 participants. 
The standard deviation for the random intercept was 1.30 (what does this indicate about between individual differences?).
Using Satterthwaite's approximation for degrees of freedom revealed that placebo and its interactions with a variety of electrodes had a significant effect on slow wave density(p < .05).

