---
title: "SWS_Dynamics_v1"
author: "Elaine P."
date: "22/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(ggplot2)
library(ggpubr)
library(car)
library(haven)
library(data.table)
library(visreg)
library(dplyr)
library(tidyr)
library(reshape2)
library(rstatix)
library(JWileymisc)
library(lme4)
library(lmerTest)
library(multilevelTools)
library(tidyverse)
library(Rmisc)

SWS_data4 <- read.table("../Tables/CTET_SWdetection_thr90_byE_P2P_avDens_behav_vec_full_v3.txt", header = TRUE, sep = ",", stringsAsFactors = FALSE)

names(SWS_data4)[names(SWS_data4) == "Drug"] <- "Treatment"

SWS_data4$Treatment<-as.factor(SWS_data4$Treatment)

SWS_data4$Treatment<-relevel(SWS_data4$Treatment,"PLA")

```

```{r} 

all_lme_block = list()
for (nBlock in seq(1,10))
{lme_block <- lmer(SWdens ~ 1 + Treatment + (1|SubID), REML = TRUE, data = SWS_data4[SWS_data4$BlockN == nBlock,])
all_lme_block[[length(all_lme_block)+1]] = lme_block
}

summary(all_lme_block[[1]])
summary(all_lme_block[[2]])
summary(all_lme_block[[3]])
summary(all_lme_block[[4]])
summary(all_lme_block[[5]])
summary(all_lme_block[[6]])
summary(all_lme_block[[7]])
summary(all_lme_block[[8]])
summary(all_lme_block[[9]])
summary(all_lme_block[[10]])

```


```

```{r} 

#lme_treatment <- lmer(SWdens ~ 1 + BlockN + (1|SubID), REML = TRUE, data = SWS_data4[SWS_data4$Treatment == 'PLA',])
#summary(lme_treatment)

lme_treatment <- lmer(SWdens ~ 1 + Treatment*BlockN + (1|SubID), REML = TRUE, data = SWS_data4[SWS_data4$Treatment == 'CIT' | SWS_data4$Treatment == 'PLA',])
summary(lme_treatment)

lme_treatment <- lmer(SWdens ~ 1 + Treatment*BlockN + (1|SubID), REML = TRUE, data = SWS_data4[SWS_data4$Treatment == 'ATM' | SWS_data4$Treatment == 'PLA',])
summary(lme_treatment)

lme_treatment <- lmer(SWdens ~ 1 + Treatment*BlockN + (1|SubID), REML = TRUE, data = SWS_data4[SWS_data4$Treatment == 'MPH' | SWS_data4$Treatment == 'PLA',])
summary(lme_treatment)

```