---
title: "VAS - Alertness (ANOVA)"
output: html_document
---


```{r}
library(ggplot2)
library(ggpubr)
library(car)
library(haven)
library(data.table)
library(visreg)
library(dplyr)
library(tidyr)
library(reshape2)
library(reshape)
library(rstatix)
library(readxl)

VAS_alertness_exclusions <- read_excel("../Tables/VAS_alertness_exclusions.xlsx")

VAS_alertness_exclusions <- select(VAS_alertness_exclusions, -c(1,...15, ...16))

names(VAS_alertness_exclusions) <- c("Participant","MPH_1", "MPH_2", "MPH_3", "ATM_1", "ATM_2", "ATM_3", "CIT_1", "CIT_2", "CIT_3", "PLA_1", "PLA_2", "PLA_3")

VAS_alertness_exclusions$Participant <- as.factor(VAS_alertness_exclusions$Participant)

alertness.long <- melt(as.data.frame(VAS_alertness_exclusions), id.vars = "Participant", variable.name = "condition", value.name = "score")

names(alertness.long)[names(alertness.long) == "variable"] <- "condition"
names(alertness.long)[names(alertness.long) == "value"] <- "score"
```

``` {r}
## mean and sd
alertness.long %>% group_by(condition) %>% get_summary_stats(score, type = "mean_sd")
alertness.mean <- ggplot(alertness.long, aes(condition, score)) +
    stat_summary(fun.data = mean_cl_normal) +
    theme_pubr()
print(alertness.mean)

##outliers
alertness.long %>% group_by(condition) %>% identify_outliers(score)

## identifying and renaming NAs
alertness.long[alertness.long == 0.00000] <- NA
alertness.long %>% group_by(condition) %>% identify_outliers(score)

alertness.long %>%
  group_by(condition) %>%
  shapiro_test(score)
ggqqplot(alertness.long, "score", facet.by = "condition")
```
 
 PLA-2 was not normally distributed according to Shapiro-Wilk (p was 0.0396), but, upon careful inspection of the QQ-plot, it does not stray from the proposed normal distribution 


```{r}
##One-Way ANOVA Test
alertness.anova <- anova_test(alertness.long, score ~ condition, dv = score, wid = Participant)
get_anova_table(alertness.anova)

pwc.alertness <- alertness.long %>% pairwise_t_test(score ~ condition, paired = TRUE, p.adjust.method = "bonferroni")
pwc.alertness

```

Significant differences were found for: MPH-1 and ATM-3, MPH-1 and CIT-3, MPH-1 and PLA-3, MPH-2 and ATM-3, MPH-2 and CIT-3, MPH-2 and PLA-2, MPH-2 and PLA-3, MPH-3 and ATM-3, MPH-3 and CIT-3, MPH-3 and PLA-3, ATM-1 and ATM-3, ATM-1 and CIT-3, ATM-1 and PLA-3, ATM-2 and ATM-3, ATM-2 and CIT-3, ATM-2 and PLA-3, ATM-3 and CIT-1, ATM-3 and CIT-2, ATM-3 and PLA-1, CIT-1 and CIT-3, CIT-1 and PLA-3, CIT-2 and CIT-3, CIT-2 and PLA-3, CIT-3 and PLA-1, CIT-3 and PLA-2, PLA-1 and PLA-3, PLA-2 and PLA-3



#REDO AFTER REMOVAL OF NAs

```{r}
##removal of participant with 4 as they have NAs coded 
alertness.long.NoNA <-na.omit(alertness.long)

##check there are no NAs
complete.cases(alertness.long.NoNA)
summary(alertness.long.NoNA)

##new mean and SD
alertness.long.NoNA %>% group_by(condition) %>% get_summary_stats(score, type = "mean_sd")
alertness.mean1 <- ggplot(alertness.long.NoNA, aes(condition, score)) +
    stat_summary(fun.data = mean_cl_normal) +
    theme_pubr()
print(alertness.mean1)

##outliers
alertness.long.NoNA %>% group_by(condition) %>% identify_outliers(score)

##normality 
alertness.long.NoNA %>%
  group_by(condition) %>%
  shapiro_test(score)
ggqqplot(alertness.long.NoNA, "score", facet.by = "condition")

## linearity assumption 
library(GGally)
linearity.alertness <- alertness.long.NoNA %>%
  select(score, condition) %>%
  group_by(condition) %>%
  doo(~ggpairs(.) + theme_bw(), result = "plots")
linearity.alertness

linearity.alertness$plots

## homogeneity of variance 
leveneTest(score ~ condition, data = alertness.long.NoNA)
```

- No change in mean or SD was found from the removal of NA values 
- No outliers were found 
- Same graphs obtained for normality 
- Insignificant results were obtained for Levene's test and thus, homogeneity of variance was not violated 

```{r}
##Re-run of The One-Way ANOVA Test
alertness.anova1 <- anova_test(alertness.long.NoNA, score ~ condition, dv = score, wid = Participant)
get_anova_table(alertness.anova1)

##Pair-wise T-test
pwc.alertness1 <- alertness.long.NoNA %>% pairwise_t_test(score ~ condition, paired = FALSE, p.adjust.method = "bonferroni")
pwc.alertness1

```

Some differences observed in pair-wise t-test from this time compared to last time 


NOW CONDUCTING TWO-WAY REPREATED MEASURES ANOVA 
``` {r}
## separate condition and time into two different columns
 alertness.long.NoNA <- separate(alertness.long.NoNA, "condition", c("condition", "time"))

##change condition and time to factors 
alertness.long.NoNA$time <- as.factor(alertness.long.NoNA$time)
alertness.long.NoNA$condition <- as.factor(alertness.long.NoNA$condition)
str(alertness.long.NoNA)

## summary statistics 
sum.alertness <- alertness.long.NoNA%>%
  group_by(condition, time) %>%
  get_summary_stats(score, type = "mean_sd")
sum.alertness

##boxplot
bxp.alertness <- ggboxplot(
  alertness.long.NoNA, x = "condition", y = "score",
  color = "time", palette = "jco")
bxp.alertness

##outliers 
alertness.long.NoNA %>%
  group_by(condition, time) %>%
  identify_outliers(score)

##normality assumption 
alertness.long.NoNA %>%
  group_by(condition, time) %>%
  shapiro_test(score)

ggqqplot(alertness.long.NoNA, "score", ggtheme = theme_bw()) +
  facet_grid(time ~ condition, labeller = "label_both")

```
-no extreme outliers were found, thus none will be removed 
- PLA-2 was again found to violate normality according to shapiro-whilk, but inspection of the qqplot proved otherwise


```{r}
##two-way repeated measures ANOVA 
alertness.aov <- anova_test(
  data = alertness.long.NoNA, dv = score, wid = Participant,
  within = c(condition, time))
get_anova_table(alertness.aov)

## Effect of condition at each time point
one.way.alertness <- alertness.long.NoNA %>%
  group_by(time) %>%
  anova_test(dv = score, wid = Participant, within = condition) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "bonferroni")
one.way.alertness
# Pairwise comparisons between condition groups
pwc.alertness.2 <- alertness.long.NoNA %>%
  group_by(time) %>%
  pairwise_t_test(
    score ~ condition, paired = FALSE,
    p.adjust.method = "bonferroni")
pwc.alertness.2

# Effect of time at each level of condition
one.way2 <- alertness.long.NoNA %>%
  group_by(condition) %>%
  anova_test(dv = score, wid = Participant, within = time) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "bonferroni")
one.way2

# Pairwise comparisons between time points
pwc2 <- alertness.long.NoNA %>%
  group_by(condition) %>%
  pairwise_t_test(
    score ~ time, paired = TRUE,
    p.adjust.method = "bonferroni"
    )
pwc2
```
-condition was found to be significant only at times 2 and 3 (not 1)
-pairwise comparison shows that the mean self-esteem score was significantly different between ATM and MPH at time 3 (p = .007), CIT and MPH at time 3 (p = .000296), and MPH and PLA at time 3 (p = .000606).
-for time, a few effects were found to be significant

```{r}
names(alertness.long.NoNA)[2] <- "Treatment"
alertness.long.NoNA$Treatment<-ordered(alertness.long.NoNA$Treatment,c("PLA","MPH","ATM","CIT"))


ggplot(alertness.long.NoNA, aes(x = time, y = score, fill = Treatment)) +
  geom_flat_violin(aes(fill = Treatment), position = position_nudge(x = .1, y = 0), adjust = 1.5, trim = FALSE, alpha = .25, colour = NA) +
  geom_point(aes(x = as.numeric(time)-.225, y = score, colour = Treatment), position = position_jitter(width = .05), size = .25, shape = 20)  + geom_boxplot(aes(x = time, y = score, fill = Treatment), outlier.shape = NA, alpha = .5, width = .225, colour = "black") +
  geom_line(data = sum.alertness, aes(x = as.numeric(time)+.1, y = mean, group = Treatment, colour = Treatment), linetype = 3, size = .6) + geom_point(data = sum.alertness, aes(x = as.numeric(time)+.1, y = mean, group = Treatment, colour = Treatment), shape = 18) + scale_fill_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) + scale_colour_manual(values = c("#666666", "#d95f02", "#7570b3", "#1b9e77")) +xlab("Timepoints") + ylab("Alertness Scores") + theme(panel.background = element_blank(), axis.line = element_line(colour = "black")) + ylim(0, 100) 


#  +ggtitle("Reported levels of alertness across time and Treatment")


ggsave(file="../Figures/VAS_Plot.png", dpi = 600, 
       width = 20,
      height = 15,
    units = c("cm"))



```
** got rid of SE because my stats summary didnt have it 
- it was used for ymin = mean-se, ymax = mean + se for the geom_errorbar
**took out error_bar


*** if probem occurs in geom_flat_violin : type in console: source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R") )